
% Preamble
\documentclass[a4paper]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}

\geometry{margin=1in}

\definecolor{usafablue}{RGB}{0,48,143}
\definecolor{usafagrey}{RGB}{166,166,168}
\hypersetup{colorlinks=true,urlcolor=usafablue}


% \newcommand{\github}{\url{github.com/brandondbutcher}}
\newcommand{\biostat}{\href{https://www.public-health.uiowa.edu/biostat/}{Biostatistics}}
\newcommand{\deptbiostat}{\href{https://www.public-health.uiowa.edu/biostat/}{Department of Biostatistics}}
\newcommand{\uiowa}{\href{https://www.uiowa.edu}{University of Iowa}}
\newcommand{\advisor}{\href{https://www.public-health.uiowa.edu/people/brian-smith/}{Brian J. Smith, Ph.D.}}
\newcommand{\isu}{\href{https://www.iastate.edu/}{Iowa State University}}
\newcommand{\stat}{\href{https://stat.iastate.edu/}{Statistics}}
\newcommand{\deptstat}{\href{https://stat.iastate.edu/}{Department of Statistics}}
\newcommand{\jakscholar}{\href{https://www.stat.iastate.edu/undergraduate-scholarship-and-awards}{J.A.K. Scholarship in Statistics}}
\newcommand{\psych}{\href{https://psychology.iastate.edu/}{Psychology}}
\newcommand{\LinkedIn}{\href{https://www.linkedin.com/in/brandon-butcher-72250153/}{LinkedIn}}
\newcommand{\ResearchGate}{\href{https://www.researchgate.net/profile/Brandon_Butcher}{ResearchGate}}
\newcommand{\GitHub}{\href{https://github.com/brandondbutcher}{GitHub}}


% Begin CV
\begin{document}


% Name
\begin{center}
  \Huge\textsc{Brandon D. Butcher}
  \textcolor{usafagrey}{\rule{\textwidth}{1pt}}
\end{center}


% Contact info
\begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}lr}
  Department of Biostatistics & Email: \texttt{brandon-butcher@uiowa.edu} \\
  University of Iowa & Phone: \texttt{319-930-2609} \\
  145 North Riverside Dr.  & Web: \GitHub, \LinkedIn, \ResearchGate \\
  N365 CPHB & \\
  Iowa City, IA 52242 &  \\
\end{tabular*}
\vspace{\baselineskip}


% Education
\begin{flushleft}
  \Large\textsc{Education}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-\baselineskip}

\begin{tabular*}{0.96\textwidth}{@{\extracolsep{\fill}}clr}
  Spring 2020 & Ph.D. Biostatistics & University of Iowa \\
 (\textit{expected}) & \multicolumn{2}{l}{Thesis: \textit{Bayesian Tree-Based Methods for
      Statistical Learning \& Predictive Inference}} \\
   & Advisor: Brian J. Smith, Ph.D. & \\[3pt]
  2016 & M.S. Biostatistics & University of Iowa \\
   & \multicolumn{2}{l}{
    Preceptorship: \textit{
      A decision support system for Parkinson's clinical trial design
   }} \\
   & Advisor: Brian J. Smith, Ph.D. & \\[3pt]
  2012 & B.S. Statistics & Iowa State University \\
  2010 & B.S. Psychology & Iowa State University
\end{tabular*}
\vspace{0.25\baselineskip}


% Professional Experience
\begin{flushleft}
  \Large\textsc{Professional Experience}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-\baselineskip}

\begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}clr}
  2016--\textit{present} & Graduate Research Assistant & University of Iowa \\
   & Injury Prevention Research Center & \\
   & College of Public Health & \\[3pt]
  Summer 2019 & Summer Intern & ACT, Inc. \\
    & Validity \& Efficacy Research Group & \\
    & Iowa City, IA & \\[3pt]
  2015--2016 & Graduate Research Assistant & University of Iowa \\
   & Department of Obstetrics and Gynecology & \\
   & Carver College of Medicine & \\
  2012--2015 & Data Analyst & University of Iowa \\
   & Department of Psychiatry & \\
   & Carver College of Medicine & \\[3pt]
  2012 & Grading Assistant & University of Iowa \\
   & Department of Statistics & \\
   & College of Liberal Arts and Sciences & \\[3pt]
  2010--2012 & Research Assistant & Iowa State University \\
   & Center for Industrial Research and Service \\
   & College of Engineering &
\end{tabular*}
\vspace{0.25\baselineskip}


% Publications
\begin{flushleft}
  \Large\textsc{Publications}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-1.5\baselineskip}

\begin{enumerate}

  % \item[14.] Conrad, A., \textbf{Butcher, B.}, Resmiye, O., Ronnenberg, M.,
  %   Peek-Asa, C. (\textit{submitted}). Trends in shaken baby
  %   syndrome diagnoses among young children hospitalized for abuse.
  %   \textit{Pediatrics}.

  % \item[13.] Wojciak, A., \textbf{Butcher, B.}, Conrad-Hiebner, A., Coohey, C.,
  %   Resmiye, O., Peek-Asa, C. (\textit{submitted}). National Trends in Child
  %   Abuse and Neglect Hospitalization Rates and Costs.
  %   \textit{JAMA Pediatrics}.

  \item[12.] Hamann, C., \textbf{Butcher, B.}, Wu, H., Peek-Asa, C. (\textit{submitted}).
    Driver histories, charges, and convictions in bicycle- and pedestrian-motor
    vehicle crashes. \textit{Accident Analysis \& Prevention}.

  \item[11.] Hamann, C., Schwab-Reese, L., O'Neal, E., \textbf{Butcher, B.},
    Yang, J., Peek-Asa, C. (2019+). Family communication
    patterns and teen driving intervention effectiveness.
    \textit{American Journal of Health Behavior}.

  \item[10.] Peek-Asa, C., Reyes, M., Hamann, C., \textbf{Butcher, B.},
    Cavanaugh, J. (2019+). A randomized trial to test the impact
    of parent engagement on improving in-vehicle feedback systems.
    \textit{Accident Analysis \& Prevention}.

  \item[9.] Kellog, L., \textbf{Butcher, B.}, Peek-Asa, C., Wibbenmeyer, L. (2018).
    The impact of legislation on gas can- and mattress-related
    burn injuries. \textit{Journal of Burn Care \& Research}, 39(1), 21--29.

  \item[8.] Peek-Asa, C., \textbf{Butcher, B.}, Cavanaugh, J. (2017). Cost of the
    hospitalization for firearm injuries by firearm type, intent, and
    payer in the United States. \textit{Injury Epidemiology}, 4(1), 20.

  \item[7.] Coryell, W., Yolken, R., \textbf{Butcher, B.}, Burns, T., Dindo, L., Schlechte,
    J., Calarge, C. (2016). Toxoplasmosis titers and past suicide attempts among
    older adolescents. \textit{Archives of Suicide Research}, 20(4), 605--613.

  \item[6.] Deumic, E., \textbf{Butcher, B.}, Clayton, A., Dindo, L., Burns, T., Calarge,
    C. (2016). Sexual functioning in adolescents with major depressive disorder.
    \textit{Journal of Clinical Psychiatry}, 77(7), 957--962.

  \item[5.] Coryell, W., \textbf{Butcher, B.}, Burns, T., Dindo, L., Schlechte, J.,
    Calarge, C. (2016). Fat distribution and major depressive disorder in
    late adolescence. \textit{Journal of Clinical Psychiatry}, 77(1), 84--89.

  \item[4.] Coryell, W., Kriener, A., \textbf{Butcher, B.}, Nurnberger, J., McMahon, F.,
    Berrettini, W., Fiedorowicz, J. (2016). Risk factors for suicide in bipolar
    I disorder in two prospectively studied cohorts. \textit{Journal of Affective
    Disorders}, 190, 1--5.

  \item[3.] Bahr, S., Tyler, B., Wooldridge, N., \textbf{Butcher, B.}, Burns, T., Teesch, L.,
    Oltman, C., Azcarate-Peril, M.A., Kirby, J., Calarge, C. (2015).
    \textit{Nature Translational Psychiatry}, 5(10), e652.

  \item[2.] Calarge, C., \textbf{Butcher, B.}, Burns, T., Coryell, W., Schlechte, J., Zemel,
    B. (2014). Major depressive disorder and bone mass in adolescents and young
    adults. \textit{Journal of Bone and Mineral Research}, 29(10), 2230--2237.

  \item[1.] Fiedorowicz, J., Jancic, D., Potash, J., \textbf{Butcher, B.}, Coryell, W.
    (2014). Vascular mortality in participants of a bipolar genomics study.
    \textit{Psychosomatics}, 55(5), 485--490.

\end{enumerate}


% Conference Presentations
\begin{flushleft}
  \Large\textsc{Conference Presentations}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-1.5\baselineskip}

\begin{enumerate}

  \item[10.] \textbf{Butcher, B.}, Hamann, C., Reyes, M., Peek-Asa, C. (2019).
    Identifying high risk adolescent drivers: Agreement between self-report
    and in-vehicle kinematic event recorders. Poster.
    \textit{Transportation Research Board Annual Meeting}. Washington, D.C.

  \item[9.] \textbf{Butcher, B.} and Smith B.J. (2018). A modified approach
    to component-wise gradient boosting for high-dimensional regression models.
    Oral. \textit{Joint Statistical Meetings}. Vancouver, British Columbia, CA.

  \item[8.] \textbf{Butcher, B.} and Smith, B.J. (2018). A novel approach to
    component-wise gradient boosting for high-dimensional linear models.
    Poster. \textit{Conference on Predictive Inference and its Applications}.
    Iowa State University, Ames, IA.

  \item[7.] \textbf{Butcher, B.}, Breheny, P., Dai, D. (2016).
    High-dimensional Cox regression for genome-wide assessment of the prognostic
    benefit of somatic mutations in ovarian cancer. Poster.
    \textit{Joint Statistical Meetings}. Chicago, IL.

  \item[6.] Calarge, C., \textbf{Butcher, B.}, Coryell, W., Fiedorowicz, J.,
    Burns, T. (2014). Low bone mass predicts persistence of depresssion in
    adolescents. Poster. \textit{Annual meeting of the
    American Academy of Chilad and Adolescent Psychiatry}. San Antonio, TX.

  \item[5.] Deumic, E., \textbf{Butcher, B.}, Clayton, A., Calarge, C. (2014).
    Depression and sexual functioning in adolescents. Poster. \textit{Annual meeting of the
    American Academy of Chilad and Adolescent Psychiatry}. San Antonio, TX.

  \item[4.] Coryell, W., \textbf{Butcher, B.}, Burns, T., Dindo, L., Schlechte, J.,
    Calarge, C. (2014). Fat distribution and major depressive disorder in late
    adolescence. Poster. \textit{Annual meeting of the Society for Biological Psychiatry}.
    New York, NY.

  \item[3.] Calarge, C., \textbf{Butcher, B.}, Schlechte, J., Burns, T. (2013).
    Depression and bone mass in adolescents. Poster. \textit{Annual meeting of the
    American Academy of Chilad and Adolescent Psychiatry}. Orlando, FL.

  \item[2.] Calarge, C., \textbf{Butcher, B.}, Burns, T., Haynes, W., Schlechte,
    J., Coryell, W. (2013). Depression and body fat distribution in adolescents.
    Poster. \textit{Annual meeting of the American Academy of Child and Adolescent
    Psychiatry}. Orlando, FL.

  \item[1.] \textbf{Butcher, B.}, Khounlavouth, A., Tuhn, S., Quinlivan, D.,
    Wilford, M., Benal, J., Baron, B., Wells, G. (2010). Eyewitness accuracy for
    single- versus multiple-perpetrator crimes: Not quite common sense. Poster.
    \textit{Annual convention of the Association for Psychological Science}.
    Boston, MA.

\end{enumerate}

% Statistical Software
\begin{flushleft}
  \Large\textsc{Statistical Software}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-1.5\baselineskip}

\begin{enumerate}
  \item[3.] \textbf{Butcher, B.}. BART.jl: Bayesian
    additive regression trees, julia software package.
    \url{https://github.com/brandondbutcher/BART.jl}
  \item[2.] Smith, B.J., \textbf{Butcher, B.}, Peterson, R.A. (2016).
    Parkinson's Clinical Trials Design Tool, R Shiny software application.
    \url{https://github.com/brian-j-smith/PPMITrialDesign}
  \item[1.] Breheny, P., \textbf{Butcher, B.}, Hunsicker, L. (2018).
    \texttt{AUC.cv.ncvsurv}: function to compute cross-validated
    AUC for Cox regression models. \texttt{ncvreg}: Regularization Paths for SCAD
    and MCP Penalized Regression, R software package, version 3.11-0.
    \textit{The Comprehensive R Archive Network}.
    \url{https://cran.r-project.org/package=ncvreg}
\end{enumerate}


% Awards
\begin{flushleft}
  \Large\textsc{Awards}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-\baselineskip}

\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cll}
  2017 & Leon Burmeister Memorial Scholarship & University of Iowa \\
       & Department of Biostatistics & \\[3pt]
  % 2012 & Statistical Quality Assurance Poster Competition & Iowa State University \\
  %     & Dept. of Industrial and Manufacturing Systems Engineering & \\
  %     & $2^{nd}$ Place & \\[3pt]
  2011--2012 & J.A.K. Scholarship in Statistics & Iowa State University \\
            & Department of Statistics
\end{tabular*}
\vspace{0.25\baselineskip}


% Computing Experience
\begin{flushleft}
  \Large\textsc{Computing Experience}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-1.5\baselineskip}

\begin{itemize}
  \item Scientific Programming: C/C++, Julia, R, RStudio Shiny, SAS
  \item Scripting Languages: BASH
  \item Data Management: Microsoft Access, SQL
  \item Markup Languages: HTML, knitr, \LaTeX, Markdown, RMarkdown
  \item Version Control: git
\end{itemize}


% Freelance Experience
\begin{flushleft}
  \Large\textsc{Freelance Experience}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-1.5\baselineskip}

\begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}ccc}
  2018--\textit{present} & Statistical Consultant & Kanchna Ramchandran, Ph.D. \\
\end{tabular*}
\begin{itemize}[itemsep = 0.3ex, leftmargin = 1cm]
  \item Consult on appropriate statistical methodology for Dr. Ramchandran's neuroscience research
  \item Explain various statistical methods including: mixed effects models, penalized regression, Bayesian methods, resampling methods, among others
  \item Provide R programming for statistical analyses
  \item Developed custom R package for automating exploratory analyses.
\end{itemize}
\vspace{0.25\baselineskip}

\begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}ccc}
  2018--\textit{present} & Tutor & University of Iowa  \\
\end{tabular*}
\begin{itemize}[itemsep = 0.3ex, leftmargin = 1cm]
  \item Fall 2018, Applied Categorical Data Analysis
  \begin{itemize}[itemsep = 0.3ex]
    \item Tutored 3 Ph.D. students in applied categorical course for non-biostatistics majors.
    \item Topics covered: analysis of proportions, risk measures, measures of association,
      Mantel-Haenszel methods, logistic regression for binary responses and matched data,
      logistic regression for multi-category responses, Poisson and negative-binomial
      regression, generalized estimating equations and generalized linear mixed effects models.
  \end{itemize}
  \item Spring 2018, Regression \& ANOVA in Health Sciences:
  \begin{itemize}[itemsep = 0.3ex]
    \item Tutored Ph.D. student in applied regression course for non-biostatistics majors.
    \item Topics covered: correlation, single and multiple linear regression, confounding, interactions, model building,
      single and multiple factor ANOVA, contrasts, mutliple comparisons, nested and block designs, and introduction to
      mixed models.
  \end{itemize}
\end{itemize}
\vspace{0.25\baselineskip}

%  Graduate Coursework
\begin{flushleft}
  \Large\textsc{Ph.D. Coursework}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-1.5\baselineskip}

\begin{itemize}
  \item Theory of Biostatistics I \& II
  \item Linear Models
  \item Survival Data Analysis
  \item Analysis of Categorical Data
  \item Longitudinal Data Analysis
  \item Bayesian Methods and Design
  \item Computer Intensive Statistics (taught by \href{https://github.com/brandondbutcher}{Luke Tierney})
  \item Advanced Biostatistics Seminar: Statistical Methods in Bioinformatics
  \item Advanced Biostatistics Seminar: Model Selection
  \item Advanced Biostatistics Seminar: Advanced Biostatistical Computing
  \item Advanced Biostatistics Seminar: Statistical Analysis of Network Data
\end{itemize}


% Professional Affiliations & Service
\begin{flushleft}
  \Large\textsc{Professional Affiliations \& Service}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-1.5\baselineskip}

\begin{itemize}
  \item University of Iowa:
  \begin{itemize}
    \item Department of Biostatistics:
    \begin{itemize}
      \item Computing Committee: Student Representative, 2018--2019
      \item Biostatistics Student Organization: BSAC Coordinator, 2015--2016
    \end{itemize}
    \item College of Public Health
    \begin{itemize}
      \item Awards Committee: Department of Biostatistics Student Representative, 2018--2019
      \item Board of Advisors Meeting: Department of Biostatistics Student Representative, 2018
    \end{itemize}
  \end{itemize}
  \item American Statistical Association: Member, 2014--\textit{present}
\end{itemize}

\newpage

% References
\begin{flushleft}
  \Large\textsc{References}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-\baselineskip}

\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}ll}
  Brian J. Smith, Ph.D.              & Joseph Cavanaugh, Ph.D.\\
  Professor                          & Professor \\
  Department of Biostatistics        & Department of Biostatistics \\
  University of Iowa                 & University of Iowa \\
  145 North Riverside Drive          & 145 North Riverside Drive \\
  N344 CPHB                          & N332A CPHB \\
  Iowa City, IA 52242                & Iowa City, IA 52242 \\
  \texttt{brian-j-smith@uiowa.edu}   & \texttt{joe-cavanaugh@uiowa.edu} \\
  \texttt{319-384-1587}              & \texttt{319-384-1602} \\[10pt]
  Patrick Breheny, Ph.D.             & Corinne Peek-Asa, Ph.D.\\
  Associate Professor                & Professor \\
  Department of Biostatistics        & Department of Occupational \& Environmental Health \\
  University of Iowa                 & University of Iowa \\
  145 North Riverside Drive          & 145 North Riverside Drive \\
  N336 CPHB                          & S143 CPHB \\
  Iowa City, IA 52242                & Iowa City, IA 52242 \\
  \texttt{patrick-breheny@uiowa.edu} & \texttt{corinne-peek-asa@uiowa.edu} \\
  \texttt{319-384-1584}              & \texttt{319-335-4895}
\end{tabular*}


% End CV
\end{document}
