
% Preamble
\documentclass[a4paper]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}

\definecolor{usafablue}{RGB}{0,48,143}
\definecolor{usafagrey}{RGB}{166,166,168}
\hypersetup{colorlinks=true,urlcolor=usafablue}

\newcommand{\github}{\url{github.com/brandondbutcher}}
\newcommand{\biostat}{\href{https://www.public-health.uiowa.edu/biostat/}{Biostatistics}}
\newcommand{\deptbiostat}{\href{https://www.public-health.uiowa.edu/biostat/}{Department of Biostatistics}}
\newcommand{\uiowa}{\href{https://www.uiowa.edu}{University of Iowa}}
\newcommand{\advisor}{\href{https://www.public-health.uiowa.edu/people/brian-smith/}{Brian J. Smith, Ph.D.}}
\newcommand{\isu}{\href{https://www.iastate.edu/}{Iowa State University}}
\newcommand{\stat}{\href{https://stat.iastate.edu/}{Statistics}}
\newcommand{\deptstat}{\href{https://stat.iastate.edu/}{Department of Statistics}}
\newcommand{\jakscholar}{\href{https://www.stat.iastate.edu/undergraduate-scholarship-and-awards}{J.A.K. Scholarship in Statistics}}
\newcommand{\psych}{\href{https://psychology.iastate.edu/}{Psychology}}

% \usepackage{array}
% \newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
% \newcolumntype{R}{p{0.8\textwidth}}
% \newcommand\VRule{\color{usafagrey}\vrule width 0.5pt}

% Begin CV
\begin{document}

% Name
\begin{center}
  \Huge\textsc{Brandon D. Butcher}
  \textcolor{usafagrey}{\rule{\textwidth}{1pt}}
\end{center}

% Contact info
\begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}lr}
  N365 & \texttt{brandon-butcher@uiowa.edu} \\
  145 North Riverside Dr.  & \texttt{\github} \\
  Iowa City, IA 52242 & \texttt{319-930-2609} \\
\end{tabular*}
\vspace{\baselineskip}

% Education
\begin{flushleft}
  \Large\textsc{Education}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-\baselineskip}

\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}clr}
  2019 & Ph.D. \biostat & \uiowa \\
  (\textit{expected}) & Thesis: \textit{In progress} & \\
   & Advisor: \advisor & \\[3pt]
  2016 & M.S. \biostat & \uiowa \\
   & \multicolumn{2}{l}{
    Preceptorship: \textit{
      A decision support system for Parkinson's clinical trial design
   }} \\
   & Advisor: \advisor & \\[3pt]
  2012 & B.S. \stat & \isu \\
  2010 & B.S. \psych & \isu
\end{tabular*}
\vspace{0.25\baselineskip}

% Employment
\begin{flushleft}
  \Large\textsc{Employment}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-\baselineskip}

\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}clr}
  2016--\textit{present} & Graduate Research Assistant & \uiowa \\
   & Injury Prevention Research Center & \\
   & College of Public Health & \\[3pt]
  2015--2016 & Graduate Research Assistant & \uiowa \\
   & Department of Obstetrics and Gynecology & \\
   & Carver College of Medicine & \\[3pt]
  2012--2015 & Data Analyst & \uiowa \\
   & Department of Psychiatry & \\
   & Carver College of Medicine & \\[3pt]
  2012 & Grading Assistant & \isu \\
   & \deptstat & \\
   & College of Liberal Arts and Sciences & \\[3pt]
  2010--2012 & Research Assistant & \isu \\
   & Center for Industrial Research and Service \\
   & College of Engineering &
\end{tabular*}
\vspace{0.25\baselineskip}

% Publications
\begin{flushleft}
  \Large\textsc{Publications}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-1.5\baselineskip}

\begin{enumerate}

  \item Kellog, L., Butcher, B., Peek-Asa, C., Wibbenmeyer, L. (2018).
  The impact of legislation on gas can- and mattress-related
  burn injuries. \textit{Journal of Burn Care \& Research}, 39(1), 21--29.

  \item Peek-Asa, C., Butcher, B., Cavanaugh, J. (2017). Cost of the
  hospitalization for firearm injuries by firearm type, intent, and
  payer in the United States. \textit{Injury Epidemiology}, 4(1), 20.

  \item Coryell, W., Yolken, R., Butcher, B., Burns, T., Dindo, L., Schlechte,
  J., Calarge, C. (2016). Toxoplasmosis titers and past suicide attempts among
  older adolescents. \textit{Archives of Suicide Research}, 20(4), 605--613.

  \item Deumic, E., Butcher, B., Clayton, A., Dindo, L., Burns, T., Calarge,
  C. (2016). Sexual functioning in adolescents with major depressive disorder.
  \textit{Journal of Clinical Psychiatry}, 77(7), 957--962.

  \item Coryell, W., Butcher, B., Burns, T., Dindo, L., Schlechte, J.,
  Calarge, C. (2016). Fat distribution and major depressive disorder in
  late adolescence. \textit{Journal of Clinical Psychiatry}, 77(1), 84--89.

  \item Coryell, W., Kriener, A., Butcher, B., Nurnberger, J., McMahon, F.,
  Berrettini, W., Fiedorowicz, J. (2016). Risk factors for suicide in bipolar
  I disorder in two prospectively studied cohorts. \textit{Journal of Affective
  Disorders}, 190, 1--5.

  \item Bahr, S., Tyler, B., Wooldridge, N., Butcher, B., Burns, T., Teesch, L.,
  Oltman, C., Azcarate-Peril, M.A., Kirby, J., Calarge, C. (2015).
  \textit{Nature Translational Psychiatry}, 5(10), e652.

  \item Calarge, C., Butcher, B., Burns, T., Coryell, W., Schlechte, J., Zemel,
  B. (2014). Major depressive disorder and bone mass in adolescents and young
  adults. \textit{Journal of Bone and Mineral Research}, 29(10), 2230--2237.

  \item Fiedorowicz, J., Jancic, D., Potash, J., Butcher, B., Coryell, W.
  (2014). Vascular mortality in participants of a bipolar genomics study.
  \textit{Psychosomatics}, 55(5), 485--490.

\end{enumerate}

% Awards
\begin{flushleft}
  \Large\textsc{Awards}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}
\vspace{-\baselineskip}

\begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cll}
  2017 & Leon Burmeister Memorial Scholarship & \uiowa \\
       & \deptbiostat & \\[3pt]
  2011--2012 & \jakscholar & \isu \\
            & \deptstat
\end{tabular*}
\vspace{0.25\baselineskip}

% References
\begin{flushleft}
  \Large\textsc{References}
  \textcolor{usafagrey}{\rule[0.5\baselineskip]{\textwidth}{0.75pt}}
\end{flushleft}

% End CV
\end{document}
